
\section*{Conference Events}\addcontentsline{toc}{section}{Conference Events}
In addition to talks and poster sessions, there are several conference events that attendees are encouraged to attend.

\subsection*{Opening Reception}\addcontentsline{toc}{subsection}{Reception}
Following the Keynote and President's Address in Loewe Theater in August 5th, all attendees are welcome to the opening reception. Hors d'oeuvres, drink tickets, and a live jazz trio will be in the Rosenthal Pavilion, 10th floor of the Kimmel Center, starting at 6:45 PM.

\subsection*{Lunch Time Forums}\addcontentsline{toc}{subsection}{Lunchtime panels}
Three forums on aspect of academic life are scheduled during the lunch breaks:\\

\noindent  {\bf Grad Student Forum}\\
A panel of grad students and postdocs share their experience in navigating grad school via Q\&A, coordinated by SMPC student board member, David Baker.\\

\noindent  {\bf Early Career Forum}\\
 A panel  early career researchers share their experience getting established via Q\&A, coordinated by SMPC student board member, David Baker.\\

\noindent  {\bf Meet the Editors Panel}\\ 
This session will give an overview of trends in academic publishing with a focus on the journal {\it Music Perception}.  There will be time for Q\&A and an opportunity to meet some of the editors. Coordinated by Kate Steven, Editor of {\it Music Perception}.

\subsection*{Dinner Cruise}\addcontentsline{toc}{subsection}{Dinner Cruise}

The conference dinner cruise is on Tuesday evening. Ticket holders are encouraged to go directly from the last poster session to the port for boarding.\\ 

\noindent {\bf By Taxi}\\
Use the following address as the destination if hailing a taxi or Uber:\\
\indent Circle Line Sightseeing Cruises\\
\indent Pier 83, W 42nd St, New York, NY 10036\\

\noindent  {\bf By Subway}
\begin{itemize}
\item Walk to the W. 4th Street subway station. The closest entrance to this station from the Kimmel Center is on the corner of W. 3rd Street and 6th Avenue (5 minute walk).
\item Take an uptown (Manhattan or Queens-bound) A, C, or E train to Times Square 42nd St.
\item Navigate to 42nd Street from the subway station.
\item Walk towards 12th Avenue while traveling down 42nd Street. Pier 83 will be just past 12th Avenue on the Hudson River.
\end{itemize}
{\it Be sure to check the MTA homepage at} \url{https://new.mta.info} {\it to see if there are any service changes. An MTA worker will be available at W. 4th Street station should you have any questions or are in need of directions to Times Square}\\

\noindent  {\bf By Bus from Midtown}\\
From 42nd Street, take the M42 bus going West, directly to the Circle Line Pier. From 49th Street, take the M50 bus directly to the Circle Line Pier.


